Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them

### 2020-11-24 Manuscript/EPAWTFT.tex
Updated UMP convergence figure

Since the UHF ground state already provides a good approximation to the exact energy, the ground-state sheet of
the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
\hugh{The slow convergence observed in \ce{H2} can then be seen as this EP moves ever closer to one at larger $U/t$ values.}
Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
function \hugh{rather than improving the energy.
It is well-known that the spin-projection needed to remove spin-contamination can require non-linear combinations
of highly-excited determinants,\cite{Lowdin_1955c} and thus it is not surprising that this process proceeds 
very slowly as the perturbation order is increased.
}

>>>>

Since the UHF ground state already provides a good approximation to the exact energy, the ground-state sheet of
the UMP energy is relatively flat and the corresponding EP in the Hubbard dimer always lies outside the unit cylinder.
\hugh{The slow convergence observed in \ce{H2}\cite{Gill_1988} can then be seen as this EP 
moves closer to one at larger $U/t$ values.}
Furthermore, the majority of the UMP expansion in this regime is concerned with removing spin-contamination from the wave 
function \hugh{rather than improving the energy.
It is well-known that the spin-projection needed to remove spin-contamination can require non-linear combinations
of highly-excited determinants,\cite{Lowdin_1955c} and thus it is not surprising that this process proceeds 
very slowly as the perturbation order is increased.
}
